Modelling complex population structure using $F$-statistics and Principal Component Analysis

### 2022-01-26 fstats_pca_lewontin.tex
response no fig

However, understanding, conceptualizing and modeling this variation is far from trivial, and misconstrued models of human genetic differentiation have repeatedly been used to justify racist, eugenic and genocidal policies. Lewontin’s landmark 1972 paper on the apportionment of human genetic diversity was one of the first to quantify how little of between-population genetic variation could be attributed to ``racial'' continental-scale groupings. Over the last five decades, this view has been corroborated, refined and extended many times \citep{cann1987, cavalli-sforza1994, barbujani1997, rosenberg2002a}.

>>>>

However, understanding, conceptualizing and modeling this variation is far from trivial, particularly in a historical context in which mistaken ideas about human variation have been used to justify racist, eugenic and genocidal policies. Lewontin’s landmark 1972 paper on the apportionment of human genetic diversity was one of the first to quantify how little of between-population genetic variation could be attributed to ``racial'' continental-scale groupings. Over the last five decades, this view has been corroborated, refined and extended many times \citep{cann1987, cavalli-sforza1994, barbujani1997, rosenberg2002a}.
